Segmentation Using Attributes

### 2010-05-01 paper.tex
draft paper

\begin{figure}
\label{fig:truck}
\centering
\subfigure[]{
\label{fig:trucka}
\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
}
\subfigure[]{
\label{fig:truckb}
\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
}
\caption{Segmentation by maximizing attribute saliency.  \subref{fig:trucka} shows
the original image with any ``car'' attributes that were predicted.  $P$ is the probability
that the image contains a car.  \subref{fig:truckb} shows the segmented image after
running our segmentation tree pruning algorithm.  As extraneous regions are pruned
more car attributes are predicted and the probability that the remaining image 
contains a car increases.}
\end{figure}

In practice, however, the testing of all combinations of regions to find 
objects is intractable.  We use two approximatory algorithms operating on
a segmentation hierarchy to determine salient regions.  Both are subtractive
algorithms, which first predict attributes on the entire region and then
proceed by observing the effects of removing different regions during
a top-down traversal of the tree.  The benefit of using these methods are
that large regions that clearly don't contribute to attribute saliency
can be pruned from the tree early in the traversal.  This approach avoids
the combinatoric complexity of a full search and, even more, prunes many
regions from the segmentation tree before they even are searched, bringing
the computational complexity, in practice, to roughly $O(n)$ where $n$ is
the number of leaves in the segmentation tree.

@@

%-------------------------------------------------------------------------------
% technical approach
%-------------------------------------------------------------------------------
\section{Technical approach}
\label{sec:technical}
Our approach begins with training attribute classifiers.  We trained using
an SVM with linear kernel.  A set of training images is annotated with objects
contained in the image, bounding boxes for the objects, and attributes exhibited
by the image.  We use a subset of the features used in \cite{farhadi09}, namely
HOG, texture and color descriptors.  The HOG descriptors are quantized into 1000
kmeans centers, and the texture and color are quantized to 256 and 128 kmeans centers,
respectively.  Our features differ from \cite{farhadi09} in various ways.  We don't
use edge descriptors, nor do we generate ``sub-''histograms for 6 cells in the
image.  The presence of cell histograms would complicate matters when extracting
features from segmented regions.

Once the attribute classifiers are trained we build a segmentation tree for each
image.  We use the segmentation
approach of \cite{arbelaez09}.  This produces a hierarchical
segmentation by first detecting contours using the \emph{gPb} detector
\cite{maire08}.  Once the contours are detected, regions are discovered using a
watershed algorithm after which an Ultrametric Contour Map (UCM) is constructed,
which defines the region hierarchy.

We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
The first tree is an additive tree, where regions are subdivided into successively
smaller regions moving down in the tree.  We call it ``additive'' because the
original image can be reconstructed by adding the regions from each leaf node
together.  The figures show the nodes of the trees as containing images, but in
truth the trees contain binary masks which, when applied to the original image,
produce the shown node contents.

@@

\begin{figure*}
\label{fig:tree}
\centering
\subfigure[]{
\label{fig:treea}
\includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
}
\subfigure[]{
\label{fig:treeb}
\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
}
\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
regions into smaller and smaller regions, while the subtractive hierarchy increases
the size of the regions as smaller and smaller chunks are removed from the image.}
\end{figure*}

\subsection{Additive algorithm}

Blah, blah, blah.

Predicted probabilities are determined using standard histogram intersection 
between a pattern histogram for the given object and the predicted 
histogram for the region.

\[ P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}} \]

@@

The subtractive algorithm relies on the idea that if removing a region from
an image doesn't significantly affect the probability of the image containing
the object (which probability is obtained using the predicted attribute 
distribution) then that region can be safely removed in the final segmentation.
The algorithm itself is shown in algorithm \ref{alg:sub_prune}.

\begin{algorithm}
\begin{algorithmic}[1]
  \STATE \textbf{input:} 
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} master mask $m_m$
  \STATE \hspace{3 mm} probability $P_{root}$ on root node
  \STATE \hspace{3 mm} factor $f$
  \STATE $m_n$ := mask of $n$
  \STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
  \STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
  \IF{$P_{pred} < f P_{root}$}
    \STATE SUBTRACTIVE\_PRUNE(n.children)
  \ELSE
    \STATE $m_m = m_m \cap m_n$
  \ENDIF
\end{algorithmic}
\caption{SUBTRACTIVE\_PRUNE}
\label{alg:sub_prun}
\end{algorithm}

The subtractive algorithm begins at the root of the tree and predicts attributes.
This attribute distribution and its associated probability $P_{root}$ is assumed to be
canonical for the image.  That is, any final segmentation should not have
significantly less probability $P_{pred}$ than $P_{root}$.  The algorithm traverses
the subtractive tree depth-first, predicting on each node.  
Any node that doesn't have a significant negative effect on the probability
of the presence of the object is removed.  This test is done on line 9.  If the
predicted probability was significantly affected, then we know that the region
must remain.  But it doesn't mean that sub-regions might be able to be pruned
out.  So the procedure is called recursively, checking for smaller regions
that might be able to be pruned (line 10).

If the probability was not significantly affected, then the mask is applied
(line 12) and no recursive call is made.  This is important, because it means
that we can remove large chunks of the image wholesale and bypass predicting
on the node's posterity.

$f$ is an important parameter that requires tuning.  Increasing $f$ makes the
algorithm more conservative, that is, less likely to apply removals.  Decreasing
$f$ makes it more liberal.  We found $f=0.9$ to be a reasonable value for most images.
Figure \ref{fig:f} shows results of adjusting $f$.

@@

\begin{figure}
\centering
\subfigure[]{
\label{fig:fa}
\includegraphics[width=0.22\textwidth]{figures/parking_0.9.eps}
}
\subfigure[]{
\label{fig:fb}
\includegraphics[width=0.22\textwidth]{figures/parking_1.0.eps}
}
\caption{Result of adjusting the factor $f$ in the subtractive algorithm.
\subref{fig:fa} shows running the algorithm with $f=0.9$ and \subref{fig:fb}
shows running the algorithm with $f=1.0$.  Note that \subref{fig:fb} retains
more of the cars, especially the two closest on the right and left, but also
hsa more false-positive pixels, such as the ceiling region of the parking
garage.}
\label{fig:f}
\end{figure}

%-------------------------------------------------------------------------------
% experimental results
%-------------------------------------------------------------------------------
\section{Experimental results}
\label{sec:results}
Here are some results.
 trained using images from the pascal 
2008 dataset using the same annotations used in \cite{farhadi09}.

%-------------------------------------------------------------------------------
% conclusions and future work
%-------------------------------------------------------------------------------
\section{Conclusions and future work}
\label{sec:conclusions}
Highly dependent on attribute selection and discriminatory ability of attributes.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
\end{figure}

\begin{figure}
\centering
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
\label{fig:trucka}
}
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
\label{fig:truckb}
}
\caption{Segmentation by maximizing attribute saliency.  \subref{fig:trucka} shows
the original image with any ``car'' attributes that were predicted.  $P$ is the probability
that the image contains a car.  \subref{fig:truckb} shows the segmented image after
running our segmentation tree pruning algorithm.  As extraneous regions are pruned
more car attributes are predicted and the probability that the remaining image
contains a car increases.}
\label{fig:truck}
\end{figure}

In practice, however, the testing of all combinations of regions to
find objects is intractable.  We use two approximatory algorithms
operating on a segmentation hierarchy to determine salient regions.
Both are subtractive algorithms, which first predict attributes on
the entire region and then proceed by observing the effects of
removing different regions during a top-down traversal of the tree.
The benefit of using these methods are that large regions that
clearly don't contribute to attribute saliency can be pruned from
the tree early in the traversal.  This approach avoids the
combinatoric complexity of a full search and, even more, prunes many
regions from the segmentation tree before they even are searched,
bringing the computational complexity, in practice, to roughly
$O(n)$ where $n$ is the number of leaves in the segmentation tree.
The flowchart of our algorithm is shown in Figure
\ref{fig:flowchart}.

@@

%-------------------------------------------------------------------------------
% technical approach
%-------------------------------------------------------------------------------
\section{Attribute Detection}
\label{sec:attribute}

Attributes are high-level features which can reflect semantic properties of objects. Given the attributes, we can do object detection based on the their distribution. We use the same attribute set as \cite{farhadi09}. This set contains three types of attributes, including shape, part and material. All attributes are listed in figure \ref{fig:atts}.

\begin{figure}
\begin{tabular}{llll}
2D Boxy & 3D Boxy & Round & Vert Cyl \\
Horiz Cyl & Occluded & Tail & Beak \\
Head & Ear & Snout & Nose \\
Mouth & Hair & Face & Eye \\
Torso & Hand & Arm & Leg \\
Foot/Shoe & Wing & Propeller & Jet engine \\
Window & Row Wind & Wheel & Door \\
Headlight & Taillight & Side mirror & Exhaust \\
Pedal & Handlebars & Engine & Sail \\
Mast & Text & Label & Furn. Leg \\
Furn. Back & Furn. Seat & Furn. Arm & Horn \\
Rein & Saddle & Leaf & Flower \\
Stem/Trunk & Pot & Screen & Skin \\
Metal & Plastic & Wood & Cloth \\
Furry & Glass & Feather & Wool \\
Clear & Shiny & Vegetation & Leather \\
\end{tabular}
\caption{List of attributes trained.}
\label{fig:atts}
\end{figure}

We use similar algorithm as \cite{farhadi09} to train the attribute models. Three different type of features are used, such as HOG, texture and color descriptors\cite{farhadi09}. Those features can capture different properties. We use kmeans to quantize all the features. The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively. All the quantized features are concatenated to form the 1384 deminsional feature.

For training, we use SVM classifier with Gaussian kernel to train
model for each attribute.

%The precision of all the attributes on the test set is illustrated
%in figure?.

%Our approach begins with training attribute classifiers.  We trained using
%an SVM with linear kernel.  A set of training images is annotated with objects
%contained in the image, bounding boxes for the objects, and attributes exhibited
%by the image.  We use a subset of the features used in \cite{farhadi09}, namely
%HOG, texture and color descriptors.  The HOG descriptors are quantized into 1000
%kmeans centers, and the texture and color are quantized to 256 and 128 kmeans centers,
%respectively.  Our features differ from \cite{farhadi09} in various ways.  We don't
%use edge descriptors, nor do we generate ``sub-''histograms for 6 cells in the
%image.  The presence of cell histograms would complicate matters when extracting
%features from segmented regions.

\section{Hierarchy Segmentation}
\label{sec:segmentation}

We use the segmentation approach of \cite{arbelaez09}.  This
produces a hierarchical segmentation by first detecting contours
using the \emph{gPb} detector \cite{maire08}.  Once the contours are
detected, regions are discovered using a watershed algorithm after
which an Ultrametric Contour Map (UCM) is constructed, which defines
the region hierarchy. Some example of the hierarchy segmentation is
shown in Figure \ref{fig:tree}.

After the construction of hierarchy segmentation tree, we detect all
the attributes in each node, including the intermediate node and
leaf node. We use the output of SVM as the confidence (not binary),
so each node can be represented by the confidence distribution of
all attributes.

\section{Object Detection and Segmentation}
\label{sec:detection}

Our objective is to detect object and segment it out. In our
hierarchy segmentation tree, the problem changes to how to select
those nodes belong to the desired object. We estimate the
probability that a node is belong to object based on the attribute
confidence distribution. For each object, we manually give the
desired attribute distribution by common knowledge. We use the
histogram intersection between the desired distribution and the
estimated confidence distribution in each node as the similarity
measure. The histogram intersection is calculated as follows:

\[ HI(H_{model},H_{pred}) = \frac{|H_{model} \cap H_{pred}|}{|H_{model}|}
\] ,

where $H_{model}$ and $H_{pred}$ represent the desired attribute
distribution and predicted distribution.

To select the nodes, we propose two different top-down prune algorithms, additive algorithm and subtractive algorithm. We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
The first tree is an additive tree, where regions are subdivided into successively
smaller regions moving down in the tree.  We call it ``additive'' because the
original image can be reconstructed by adding the regions from each leaf node
together.  The figures show the nodes of the trees as containing images, but in
truth the trees contain binary masks which, when applied to the original image,
produce the shown node contents.

@@

\begin{figure*}
\centering
\subfigure[]{
\label{fig:treea}
\includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
}
\subfigure[]{
\label{fig:treeb}
\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
}
\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
regions into smaller and smaller regions, while the subtractive hierarchy increases
the size of the regions as smaller and smaller chunks are removed from the image.}
\label{fig:tree}
\end{figure*}

\subsection{Additive algorithm}
\label{ssec:additive}

This pruning algorithm is based on three observations. (1) At least
one node in the segmentation tree contrains the whole object. (This
is always true since the root node contains the whole image). (2) If
both parent node and child node have high confidence of containing
the object, the segmentation of the child node is more accurate than
that of the parrent node. (3) Even if some node has high confidence
of containing the object, its segmentation can still be improved by
removing irrelevant children node. The details of the additive
algorithm is shown in algorithm \ref{alg:add_prune}.

The idea of the algorithm is to find the smallest discriminative
regions, either positive or negative. We combine all the smallest
positive regions while remove all the negative ones to form the
final segmentation. We use three threshold for the similarity
measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent
perfect segment, positive segment and negative segment,
respectively. If the similarity is above $thre\_perf$, which means
the segmentation is perfect for the object, we cut all the nodes
below and return this segment. If the similarity is below
$thre\_neg$, which means the segment does not contain the object, we
cut all the nodes below and return NULL. If the similarity is
between $thre\_perf$ and $thre\_pos$, which means the node
definitely contains the object but the segmentation is not perfect
yet, we keep on checking its children nodes to refine the
segmentation. The final case is that the similarity is between
$thre\_pos$ and $thre\_neg$, which means we are not sure whether
there is an object in the node, so we just keep on searching its
children.

The object detection is based on the output of ADDITIVE\_PRUNE. If the output is not NULL, which means at least one node in the tree has similarity above $thre\_pos$, we think the object is detected in this image.

(We also plan to do the vertical confidence propogation. But due to the slowness of the experiment, we cannot incorporate it in this draft. We will show it in the final paper.)

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{input:}
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} desired object model $obj\_model$
  \STATE \hspace{3 mm} threshold for perfect segment $thre\_perf$
  \STATE \hspace{3 mm} threshold for positive segment $thre\_pos$
  \STATE \hspace{3 mm} threshold for negative segment $thre\_neg$
  \STATE \textbf{output:}
  \STATE \hspace{3 mm} refined segment
  \STATE
  \STATE $sim=HI(obj\_model,n.conf)$
  \IF{$sim \ge thre\_perf$}
    \STATE return $n.segment$
  \ENDIF
  \IF{$sim \le thre\_neg$}
    \STATE return $NULL$
  \ENDIF
  \STATE $s'=NULL$
  \FOR{$i=1$ to $n.childNum$}
    \STATE s\{i\}=ADDITIVE\_PRUNE(n.children\{i\},obj\_model,...
    \STATE ... thre\_perf,thre\_pos,thre\_neg)
    \STATE s'=s'+s\{i\}
  \ENDFOR
  \IF{$sim\ge thre\_pos$ and $s'==NULL$}
    \STATE return n.segment
  \ELSE
    \STATE return s'
  \ENDIF
\end{algorithmic}
\caption{ADDITIVE\_PRUNE}
\label{alg:add_prune}
\end{algorithm}

@@

The subtractive algorithm relies on the idea that if removing a region from
an image doesn't significantly affect the probability of the image containing
the object (which probability is obtained using the predicted attribute
distribution and is here used interchangably used with the term ``similarity'')
then that region can be safely removed in the final segmentation.
The algorithm itself is shown in algorithm \ref{alg:sub_prune}.

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{input:}
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} master mask $m_m$
  \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
  \STATE \hspace{3 mm} factor $f$
  \STATE \textbf{output:}
  \STATE \hspace{3 mm} $m_m$
  \STATE
  \STATE $m_n$ := mask of $n$
  \STATE $pred\_model$ := predict attributes on image($m_n \cap m_m$)
  \STATE $sim=HI(obj\_model,pred\_model)$
  %\STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
  %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
  \IF{$sim < f sim_{root}$}
    \FOR{$i=1$ to $n.childNum$}
      \STATE s\{i\}=SUBTRACTIVE\_PRUNE(n.children\{i\},$m_m$,
      \STATE ...$sim_{root}$, $f$)
    \ENDFOR
    %\STATE SUBTRACTIVE\_PRUNE(n.children)
  \ELSE
    \STATE $m_m = m_m \cap m_n$
  \ENDIF
\end{algorithmic}
\caption{SUBTRACTIVE\_PRUNE}
\label{alg:sub_prune}
\end{algorithm}

The algorithm begins at the root of the tree and predicts attributes.
This attribute distribution and its associated similarity $sim_{root}$
to the object's canonical distribution is taken to be
the standard for the image.  That is, any final segmentation should not have
significantly less similarity $sim$ than $sim_{root}$.  The algorithm traverses
the subtractive tree depth-first, predicting on each node.
Any node that doesn't have a significant negative effect on the similarity as
compared to the standard is removed.  If the
similarity was significantly affected, then we know that the region
must remain.  But it doesn't mean that sub-regions might not be able to be pruned
out, so the procedure is called recursively, checking for smaller regions
that might be able to be pruned.

If the probability was not significantly affected, then the mask is applied
and no recursive call is made.  This is important, because it means
that we can remove large chunks of the image wholesale and bypass predicting
on the node's posterity.

$f$ is an important parameter that requires tuning.  Increasing $f$ makes the
algorithm more conservative, that is, less likely to apply removals.  Decreasing
$f$ makes it more liberal.  We found $f=0.9$ to be a reasonable value for most images.
Figure \ref{fig:f} shows results of adjusting $f$ between 0.9 and 1.0.

@@

\begin{figure}
\centering
\subfigure[]{
\label{fig:fa}
\includegraphics[width=0.22\textwidth]{figures/parking_0.9.eps}
}
\subfigure[]{
\label{fig:fb}
\includegraphics[width=0.22\textwidth]{figures/parking_1.0.eps}
} \caption{Result of adjusting the factor $f$ in the subtractive
algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
that \subref{fig:fb} retains more of the cars, especially the two
closest on the right and left, but also has more false-positive
pixels, such as the ceiling region of the parking garage.}
\label{fig:f}
\end{figure}

%-------------------------------------------------------------------------------
% experimental results
%-------------------------------------------------------------------------------
\section{Experimental results}
\label{sec:results}

In this section, we evaluate our attribute based object detection
and segmentation algorithm. We will answer four questions. (1) What
is the performance of object detection and segmentation? (2) What is
the influences of different parameters? (3) What are the advantages
of the two pruning algorithms? (4) Is vertical confidence
propagation useful? (In this draft, we only have partial results, so
not all the questions are considered.)

%\subsection{Dataset}
%\label{ssec:dataset}

We use the Pascal2008 dataset. This dataset has a lot of real life
images which are more difficult to classify. The objects are labeled
by bounding boxes not accurate segmentation. For training the
attributes, we use the pascal2008 training set. The attribute
annotations used in \cite{farhadi09} are freely available and we
used them for training too. For testing the classification and
segmentation, we use the pascal2008 validation set. We plan to do
three classes classification and segmentation, including car,
aeroplane and horse. Now we only got the results on car. We will
incorporate the other classes in the final version.

Table \ref{table:aresults} shows some of the results from running
the additive algorithm on all cars in the dataset.  The recall is
the rate of correctly detecting images with cars.  The segmentation
precision is calculated with
\[ V(M_{groundtruth},M_{pred}) = \frac{|M_{groundtruth} \cap M_{pred}|}{|M_{groundtruth} \cup M_{pred}|} \]
where $M_{groundtruth}$ is the groundtruth mask calculated from the
bounding boxes stored with the annotations and $M_{pred}$ is the
predicted segmentation mask.  We of course recognize that the
bounding boxes are not a good measure of segmentation truth, but
it's the best we have available.

The segmentation precision for the additive algorithm
is far better than the precision for the subtractive algorithm (which averaged
0.09).  This is because the additive algorithm only segments images for
which it has predicted presence of a car, so that any image pruned by the
algorithm already has a high car similarity score, enhancing the segmentation.
The subtractive algorithm, on the other hand, assumes presence of a car in
the image and proceeds no matter how poor the initial similarity score is.
(For the final paper we expect to have results comparing the precision
of the two algorithms based only on images segmented by both.)

Figures \ref{fig:good_results} and \ref{fig:bad_results} show the
results of segmentations of various images by both pruning
algorithms. Figure \ref{fig:good_results} shows some good results,
while Figure \ref{fig:bad_results} shows some bad results. This
shows clear linkage between prominence of the side profile of the
car and success of the segmentation. It appears that the attribute
classifiers are more accurate on side profiles than front and rear
shots, although rear shots performed reasonably well when tail
lights were not illuminated.

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline Parameter & recall & prec \\
\hline 0.8,0.4,0.1  & 0.4317 & 0.2393 \\
\hline 0.8,0.4,0.15  & 0.3849 & 0.2370 \\
\hline 0.8,0.6,0.15  & 0.2720 & 0.2501 \\
\hline
\end{tabular}
\caption{Results from the additive algorithm on all car images.
Parameter contains the three threshold, $thre\_perf$, $thre\_pos$
and $thre\_neg$, recall is the object detection recall rate and prec
is the segmentation precision on all detected images.}
\label{table:aresults}
\end{table}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/results/2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_002198.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/a2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_002198.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/b2008_000052.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_000828.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_000952.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_002198.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{4cm} p{4cm} p{4cm} p{4cm} }
\includegraphics[width=3.95cm]{figures/results/2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_007466.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_005378.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/2008_007529.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/a2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/a2008_007466.jpg.eps} &
%\includegraphics[width=3.95cm]{figures/results/a2008_005378.jpg.eps} &
Car not detected &
\includegraphics[width=3.95cm]{figures/results/a2008_007529.jpg.eps} \\
\includegraphics[width=3.95cm]{figures/results/b2008_002483.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_007466.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_005378.jpg.eps} &
\includegraphics[width=3.95cm]{figures/results/b2008_007529.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:bad_results}
\end{figure*}

%-------------------------------------------------------------------------------
% conclusions and future work
%-------------------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}
It can be seen that in simple cases both additive and subtractive algorithms
are able to segment out rough outlines of the objects.  In most cases, even
the more difficult ones, at least part of the car was present in the final
segmentation.  This shows that the segmentation algorithms appear to be
reasonable approximations to a combinatoric approach -- that of predicting
on every combination of regions in the image.

Despite these encouraging initial results, the final segmentation region
was often not coherent.
This appears to be largely because the region tree approach is not
constrained by spatial coherence.  That is, two leaf nodes containing image
regions that are spatially next to each other may be very distant in the
region tree.  Because of this, the attribute distribution may change significantly
after considering the first node and before consideration of the second node.
Another reason for this may be that our canonical attribute distribution for
our objects gave equal weights to each attribute.  For example, a wheel was
equally as important as shininess.  This gave unfair disadvantages to
under-represented or ill-trained attributes.  This can be seen in the results
where the body of the car is removed while the wheels or headlights are
retained.

As object detection is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of car attributes were generally low.  One problem
with this implementation of attribute classifiers was that we didn't use
the selection criterion described in \cite{farhadi09} that enhances within
category prediction ability.  This means that, for example, the wheel attribute
is highly similar to the car attribute and thus its discrimative ability
is hurt.  One future direction for this research would be to improve the attribute
training using the additional selection criterion and observe effects on
the segmentations.

An interesting orthogonal direction that could be taken with these ideas is to
use segmentation using attributes as a diagnostic tool for attribute classifiers.
That is, the segmentations produced by our algorithms can help zero in on areas
in an image that exhibit high responses in detection of certain attributes.
For example, an image could be segmented using similarity to a canonical distribution
using only one attribute.  If that attribute is ``fur'' and segmentations
consistently show paws and tails, then it would quickly become clear that
the fur attribute classifier has learned on something other than fur.

The holy grail of this approach, of course, is to be able to segment objects
for which the canonical attribute distribution is unknown, based on a measure
of attribute coherence.  If this can be achieved, then segmentation experiments
could open up to non-experts, who could define coherence measures based on
semantic attributes and then could use this approach to automatically segment large
numbers of images even if no detection of their desired object exists.

Another problem with the attribute based method is that the attributes are not discriminative 
enough to separate different objects. For example, if we use the general attributes of head, torso and leg to 
do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
But those attributes can definitely separate the two objects from non-animal objects, such as car. This example demonstrates that 
attributes are helpful for the object classification, but they are not discriminative enough. So one way to deal with this is to use 
both attributes features and low level objects features for object classification. We can train a general attributes models first. 
When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.
